Ripple Protocol Consensus Algorithm Review

### 2015-05-11 paper.tex
close to finished
scale

\begin{figure}
    \centering
    \includegraphics[scale=0.3]{figures/orig-ripple.eps}
    \caption{Original Ripple Architecture}
    \label{fig:orig-ripple}
\end{figure}

\begin{figure}
    \centering
    \includegraphics[scale=0.3]{figures/ripple-labs-ripple.eps}
    \caption{Ripple Labs Architecture}
    \label{fig:ripple-labs-ripple}
\end{figure}

@@

Developer documentation about exactly how the ledger is structured is somewhat
spotty; the descriptions here are mostly based on direct analysis of the
\texttt{rippled} source code.

\begin{figure}
    \centering
    \includegraphics[scale=0.3]{figures/ledger-blockchain.eps}
    \caption{Ripple Ledger Structure}
    \label{fig:ledger-blockchain}
\end{figure}

>>>>

\begin{figure}
    \centering
    \includegraphics[scale=0.35]{figures/orig-ripple.eps}
    \caption{Original Ripple Architecture}
    \label{fig:orig-ripple}
\end{figure}

\begin{figure}
    \centering
    \includegraphics[scale=0.35]{figures/ripple-labs-ripple.eps}
    \caption{Ripple Labs Architecture}
    \label{fig:ripple-labs-ripple}
\end{figure}

@@

Detailed documentation about exactly how the ledger is structured is spotty;
the descriptions here are mostly based on direct analysis of the
\texttt{rippled} source code.

\begin{figure}
    \centering
    \includegraphics[scale=0.35]{figures/ledger-blockchain.eps}
    \caption{Ripple Ledger Structure}
    \label{fig:ledger-blockchain}
\end{figure}
